### 2021-05-31 docs/manuscript/manuscript.tex
Explicitly mention S4_Fig and S1_Table
In response to Reviewer #1, Minor Points, 2, e.

Besides topological robustness, we wanted to know if network topologies were
robust to perturbations in the values of the parameters. After performing the
perturbations to a GRN from each topology, we plotted the abundance of the
topology vs. its robustness. We did not find a significant correlation between
these two variables ($r_S = −0.0389724$, $\text{p-value} = 0.298475$)
(Fig~\ref{fig:ab-rob}A). However, when we grouped those topologies containing
the same subgraph and calculated their mean robustness, we found that between
the most robust subgraphs is the ``Bistable'' motif reported by Cotterell \&
Sharpe~\cite{Cotterell2010}, the I3-FFL and the ``Overlapping domains'' motif
(which is a variation of the I3-FFL) also reported by Cotterell \& Sharpe (see
Supplementary Material).

>>>>

Besides topological robustness, we wanted to know if network topologies were
robust to perturbations in the values of the parameters. After performing the
perturbations to a GRN from each topology, we plotted the abundance of the
topology vs. its robustness. We did not find a significant correlation between
these two variables ($r_S = −0.0389724$, $\text{p-value} = 0.298475$)
(Fig~\ref{fig:ab-rob}A). However, when we grouped those topologies containing
the same subgraph and calculated their mean robustness, we found that between
the most robust subgraphs is the ``Bistable'' motif reported by Cotterell \&
Sharpe~\cite{Cotterell2010}, the I3-FFL and the ``Overlapping domains'' motif
(which is a variation of the I3-FFL) also reported by Cotterell \& Sharpe
(see \nameref{S4_Fig} and \nameref{S1_Table}).
